ElasticBridge: Trustless Cross-Chain Bridge for Transferring Rebase Tokens

### 2021-11-29 paper.tex
Toolchain subsection

ElasticBridge --- is a proposed implementation of cross-chain bridge connecting EVM and WASM chains for exchanging rebase tokens in a decentrilized, secure and trustless fashion. The base chain that holds a ERC-20 token Contract is deployed on Ethermint network, that EVM-compatible, Proof-of-Stake and build with Cosmos SDK framework. On the other side of the bridge we got application-specific chain with WASM-based runtime powered by Substrate framework and deployed on Kusama\footnote{Biggest test network on Polkadot ecosystem, that is oriented on rapid and radical innovation. \url{https://kusama.network}} network.

@@

At the time of writing, there two prominent candidates for a EVM-to-Substrate bridge development frameworks to consider: ChainBridge\footnote{\url{https://chainbridge.chainsafe.io}} and SnowBridge\footnote{\url{https://snowbridge-docs.snowfork.com}}. Although current version of the ChainBridge operates under a trusted federation model and the SnowBridge is claimed to be trustless SPV solutions, the more likely choice out of two would still be ChainBridge, which according to ChainSafe, the developers behind the project, is a planned to move to the trustless model as well. The developers of Ampleforth currency made a similar decision for their AMPL Bridge, which is powered by Meter Passport\footnote{N-Way bridge that is build with ChainBridge framework. \url{https://docs.meter.io/passport}}.

Additionally the fact that Ethermint is a part of Cosmos ecosystem allows us use to utilize IBC protocol as well. Projects that implemented IBC for Substrate are QuantumTunnel\footnote{\url{https://github.com/ChorusOne/quantum-tunnel}} and \texttt{substrate-ibc} pallet\footnote{\url{https://github.com/octopus-network/substrate-ibc}}.

>>>>

ElasticBridge --- is a proposed implementation of cross-chain bridge connecting EVM and WASM chains for exchanging rebase tokens in a decentrilized, secure and trustless way. The base chain that holds a ERC-20 token Contract is deployed on Ethermint network, that EVM-compatible, Proof-of-Stake and build with Cosmos SDK framework. On the other side of the bridge we got application-specific chain with WASM-based runtime powered by Substrate framework and deployed on Kusama\footnote{Biggest test network on Polkadot ecosystem, that is oriented on rapid and radical innovation. \url{https://kusama.network}} network.

@@

At the time of writing, there two prominent candidates for a EVM-to-Substrate bridge development frameworks to consider: ChainBridge\footnote{\url{https://chainbridge.chainsafe.io}} and SnowBridge\footnote{\url{https://snowbridge-docs.snowfork.com}}. Although current version of the ChainBridge operates under a trusted federation model and the SnowBridge is claimed to be trustless SPV solutions, the more likely choice out of two would still be ChainBridge, which according to ChainSafe, the developers behind the project, is a planned to move to the more trustless model as well. The developers of Ampleforth made a similar decision for their AMPL Bridge as it is powered by Meter Passport\footnote{N-Way bridge that is build with ChainBridge framework. \url{https://docs.meter.io/passport}}. However, in a situation like this, rather than coping popular design decisions for a similar problem, the vision for ElasticBridge is to instead contribute in protocol implementation diversity, which provenly will make it more robust and secure.

By leveraging the fact that Ethermint is a part of Cosmos ecosystem it is also possible to use industry-proven IBC protocol. Projects that already laid foundation for IBC support on Substrate are QuantumTunnel\footnote{\url{https://github.com/ChorusOne/quantum-tunnel}} (asymmetric light client relayer) and \texttt{substrate-ibc} pallet\footnote{Substrate runtime module that brings IBC support: \href{https://github.com/octopus-network/substrate-ibc}{GitHub repository}} (native Rust implementation of IBC). Although both solutions are in early development stages, the fact that \texttt{substrate-ibc} pallet is basically a wrapper for Interchain\footnote{Foundation behind IBC protocol} approved \texttt{\href{https://github.com/informalsystems/ibc-rs}{ibc-rs}} library would most likely be a decisive for ElasticBridge's foundation.

\subsection{Specification}

ElasticBridge relies on IBC protocol to trust-lessly relay rebase token transfers\footnote{ICS20} in the multi-chain network with unknown topology. Its own role in this kind of mutual relationship is to expose Substate-based nodes containing ElasticBridge protocol runtime. These nodes together form an intermediary blockchain acting equally as service providing Parachain on Kusama network and Peg Zone between the Ethermint and other Kusama or Polkadot based Parachains. Combined security guarantees of by both sender chain's (Terndermint BFT) and receiver chain's (BABE + GRANDPA) consensus mechanism makes ElasticBridge protocol robust and allow preserve the ability to provide deterministic finality on top.
